---
title: "Untitled"
output: pdf_document
date: "2023-11-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.  

```{r}
library(rvest)
library(dplyr)
library(polite)

url <- "https://www.imdb.com/chart/toptv/?ref_=nv_tvv_250"

session <- bow(url,user_agent = "Educational Purposes")
session

```

1.  

```{r}
library(rvest)
title <- scrape(session)%>%
html_nodes("h3.ipc-title__text")%>%
html_text
title

subsettt <- as.data.frame(title[2:51])
colnames(subsettt) <- "title"
split_df <- strsplit(as.character(subsettt$ranks), ".", fixed = TRUE )
split_df<- data.frame(do.call(rbind, subsettt))
subsettt




  

```
1.
```{r}

votec <- scrape(session) %>%
  html_nodes("span.ipc-rating-star--voteCount") %>%
  html_text
subvote <- as.data.frame(votec[1:50])
colnames(subvote) <- "votecount"
split_df2 <- strsplit(as.character(subvote$voteCount), ".", fixed = TRUE )
split_df2 <- data.frame(do.call(rbind, subrate))
subvote

```


1.  

```{r}
library(rvest)
library(stringr)
rate <- scrape(session) %>%
  html_nodes("span.ipc-rating-star--imdb")  %>%
html_attr("aria-label")
rate

rate_sub<- as.data.frame(rate[2:51])
head(rate_sub)
colnames(rate_sub) <- "rate"
split_df <- strsplit(as.character(rate_sub$rate),".",fixed = TRUE)
split_df <- data.frame(do.call(rbind,split_df))


head(rate_sub)




```

1.  extract ratings

```{r}
ratesubs<- str_extract(rate_sub$rate, "\\d+\\.\\d+")
ratesubs

```
1.Temporary data frame
```{r}
wedata <- data.frame(
  Title = subsettt,
  Rate = ratesubs,
  Vote_count = voteCount
)
wedata
```
1. number of episodes
```{r}
year <- scrape(session)%>%
  html_nodes("span.sc-479faa3c-8.bNrEFi.cli-title-metadata-item") %>%
  html_text
year

2.





3. 
```{r}
ggplot(dataf, 
       aes(x = year)) +
  geom_bar(stat = "count", fill = "darkblue") +
  labs(title = "TV Shows Released by Year",
       x = "Release Year",
       y = "Number of TV Shows Released") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

# Find the year with the most TV shows released
mostTvshow <- dataf %>%
  group_by(year) %>%
  summarise(total_shows = n())

mostyear <- mostTvshow$year[which.max(mostTvshow$total_shows)]

cat("The year with the most TV shows released is ", mostyear)
```


